## Test side output

```{r}
#| output-location: column
library(palmerpenguins)
data(penguins)

penguins |> 
  ggplot(aes(x = bill_length_mm)) +
  geom_histogram()
```

## Columns

```{r}
#| layout-ncol: 2

knitr::kable(head(mtcars[, 1:2]))
knitr::kable(head(mtcars[, 3:4]))
```

## Data

The Palmer penguins

```{r}
#| eval: false
install.packages("palmerpenguins")
```

## Data

```{r}
library(palmerpenguins)
data(penguins)

knitr::kable(head(penguins))
```



## Font Awesome

{{< fa thumbs-up >}} {{< fa folder >}} {{< fa chess-pawn >}} {{< fa brands bluetooth >}} {{< fa brands twitter size=2xl >}} {{< fa brands github size=5x >}} {{< fa battery-half size=Huge >}} {{< fa envelope title="An envelope" >}}

## Code with columns

```{r}
#| echo: true
#| output-location: column-fragment
#| label: fig-airquality
#| fig-cap: Temperature and ozone level.
#| warning: false
library(ggplot2)
ggplot(airquality, aes(Temp, Ozone)) + 
  geom_point() + 
  geom_smooth(method = "loess"
)
```

This is text with [special]{style="color:red;"} formatting.

## Columns

::: {layout-ncol="2;" style="color:red;font-size:2em"}
a b
:::

## Callouts

::: callout-note
This is a note
:::

::: callout-tips
## Tip With Caption

This is a tips
:::

::: {.callout-caution collapse="true"}
This is an example of a 'folded' caution callout that can be expanded by the user. You can use `collapse="true"` to collapse it by default or `collapse="false"` to make a collapsible callout that is expanded by default.
:::

## Callouts 2

No background color.

::: {.callout-caution collapse="true" appearance="simple"}
## Pay Attention

This is an example of a 'folded' caution callout that can be expanded by the user. You can use `collapse="true"` to collapse it by default or `collapse="false"` to make a collapsible callout that is expanded by default.
:::

Or a magically [appearing word]{.fragment style="font-weight:bold;font-size:1.5em"} [with an additional point after]{.fragment}

## Options

```{r}
#| code-line-numbers: "|3"
#| eval: true
#| fig-cap: !expr glue::glue("The mean temperature was {mean(airquality$Temp) |> round()}")
#| fig-alt: |
#|   "A scatterplot with temperature by ozone levels along with a trend line
#|   indicating the increase in temperature with increasing ozone levels."
ggplot(airquality, aes(Ozone, Temp)) +
  geom_point() +
  geom_smooth(method = "loess", se = FALSE)
```

## Erratum

::: {.callout-caution collapse="true"}
## Erratum

I was wrongly using the following extent: `extent(-3837500, 3762500, -5362500, 5837500)`. [Michael Sumner](https://twitter.com/mdsumner) kindly informed me about the error. The proper extent to use is down below.
:::

# Tessst {background-color="#2C404A"}

[dsfsdf]{.callout-caution}

@MassicotteCDOM

## References

::: {#refs}
:::
